---
title: "Lab6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
	message = FALSE,
	warning = FALSE)
library(tidyverse)
library(maps)
library(mapdata)
library(lubridate)
library(viridis)
library(wesanderson)
library(RColorBrewer)
library(plotly)
```


# LAb_6: Data Maps and Interactive Graphs from the COVID-19 reporting data

1.  “COVID-19 Deaths” summarize the counts for each Country on the graph and update the graph to 9/26/2020

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

report_09_26_2020 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/09-26-2020.csv")) %>% 
  rename(Long = "Long_") %>% 
  filter(Lat != "NA") %>%  
  filter(Long != "NA") %>% 
  group_by(Country_Region) %>% 
  summarize(Confirmed = sum(Confirmed), Deaths = sum(Deaths), Lat= median(Lat), Long= median(Long))

# Read in the world map data
world <- as_tibble(map_data("world"))

world <- as_tibble(map_data("world")) %>% 
  mutate(region = str_replace_all(region, c("USA" = "US", "Czech Republic" = "Czechia",  
                                            "Ivory Coast" = "Cote d'Ivoire", "Democratic Republic of the Congo" = "Congo (Kinshasa)", 
                                            "Republic of Congo" = "Congo (Brazzaville)")))
  
# Join the covid report with the map data
country_join <- left_join(world, report_09_26_2020, by = c("region" = "Country_Region")) %>% 
  filter(Lat != "NA") %>%  
  filter(Long != "NA")

# Create the graph
ggplotly(
  ggplot(data = world, mapping = aes(x = long, y = lat, text = region, group = group)) + 
    coord_fixed(1.3) + 
    # Add data layer
    geom_polygon(data = country_join, aes(fill = Deaths), color = "black") +
    scale_fill_gradientn(colours = 
                           wes_palette("Zissou1", 100, type = "continuous")) +
    labs(title = "COVID-19 Deaths_09_26_2020")
)
```

# 2 Update Anisa Dhana’s graph layout of the US to 9/26/2020. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
report_09_26_2020_US <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/09-26-2020.csv")) %>% 
  rename(Long = "Long_") %>% 
  filter(Country_Region == "US") %>% 
  filter (!Province_State %in% c("Alaska","Hawaii", "American Samoa",
                                 "Puerto Rico","Northern Mariana Islands", 
                                 "Virgin Islands", "Recovered", "Guam", "Grand Princess",
                                 "District of Columbia", "Diamond Princess")) %>% 
  filter(Lat > 0)


# deleted trans log
mybreaks <- c(1, 100, 1000, 10000, 10000)
ggplot(report_09_26_2020_US, aes(x = Long, y = Lat, size = Confirmed)) +
  borders("state", colour = "white", fill = "grey90") +
  geom_point(aes(x=Long, y=Lat, size=Confirmed, color=Confirmed),stroke=F, alpha=0.7) +
  scale_size_continuous(name="Cases", range=c(1,7), 
                        breaks=mybreaks, labels = c("1-99",
                                                    "100-999", "1,000-9,999", "10,000-99,999", "50,000+")) +
  scale_color_viridis_c(option="viridis",name="Cases",
                        trans="log", breaks=mybreaks, labels = c("1-99",
                                                                 "100-999", "1,000-9,999", "10,000-99,999", "50,000+"))  +
  # Cleaning up the graph
  
  theme_void() + 
  guides( colour = guide_legend()) +
  labs(title = "Updated Anisa Dhana's lagout for COVID-19 Confirmed Cases in the US'") +
  theme(
    legend.position = "bottom",
    text = element_text(color = "#22211d"),
    plot.background = element_rect(fill = "#ffffff", color = NA), 
    panel.background = element_rect(fill = "#ffffff", color = NA), 
    legend.background = element_rect(fill = "#ffffff", color = NA)
  ) +
  coord_fixed(ratio=1.5)

```
The updated map is shown above.

#3 Update the above graph “Number of Confirmed Cases by US County” to 9/26/2020 and use a different color scheme or theme

```{r, echo=FALSE, message=FALSE, warning=FALSE}
report_09_26_2020 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/09-26-2020.csv")) %>% 
  rename(Long = "Long_") %>% 
  unite(Key, Admin2, Province_State, sep = ".") %>% 
  group_by(Key) %>% 
  summarize(Confirmed = sum(Confirmed)) %>% 
  mutate(Key = tolower(Key))


# get and format the map data
us <- map_data("state")
counties <- map_data("county") %>% 
  unite(Key, subregion, region, sep = ".", remove = FALSE)
# Join the 2 tibbles
state_join <- left_join(counties, report_09_26_2020, by = c("Key"))


ggplot(data = us, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  # Add data layer
  borders("state", colour = "black") +
  geom_polygon(data = state_join, aes(fill = Confirmed)) +
  scale_fill_gradientn(colors = rainbow(7),
                       breaks = c(1, 10, 100, 1000, 10000, 100000),
                       trans = "log10", na.value = "White") +
  ggtitle("Number of Confirmed Cases by US County") +
  theme_bw()
    

```

#4 Make an interactive plot using a state of your chosing using a theme different from used in the above exammples.

For this exercise I will be looking at the state of New York. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
report_09_26_2020_NY <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/09-26-2020.csv")) %>% 
  rename(Long = "Long_") %>% 
  filter(Country_Region == "US") %>%
  filter(Province_State == "New York") %>% 
  group_by(Admin2) %>% 
  summarize(Confirmed = sum(Confirmed)) %>% 
  mutate(Admin2 = tolower(Admin2))


us <- map_data("state")
ny_us <- subset(us, region == "new york")
counties <- map_data("county")
ny_county <- subset(counties, region == "new york")

state_join <- left_join(ny_county, report_09_26_2020_NY, by = c("subregion" = "Admin2")) 
# plot state map
ggplotly(
ggplot(data = ny_county, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  # Add data layer
  geom_polygon(data = state_join, aes(fill = Confirmed), color = "white") +
  scale_fill_gradientn(colors = topo.colors(10),
                       trans = "log10") +
  labs(title = "COVID-19 Confirmed Cases in New York'")+
  theme_bw()
)
```

# References 